Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-14 doc/GMP2015/s03_drp.tex
Brushed up my sections. Added new figures.

\section{Decomposition-Recombination Plan}

\begin{figure*}\centering
\begin{tikzpicture}
    \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
    \tikzstyle{e}=[]

    \node[v] (v1) at (1,1) {$R_j$};
    \node[v] (v2) at (3,1) {$R_k$};
    \node[v] (v3) at (2,2) {$D$};
    \node[v] (v4) at (2,3.3) {$R_i$};

    \tedge{v1}{v3}{solid}{}{above};
    \tedge{v2}{v3}{solid}{}{above};
    \tedge{v3}{v4}{solid}{}{right};
\end{tikzpicture}
\ldots with weights \ldots
\begin{tikzpicture}
    \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
    \tikzstyle{e}=[]

    \node[v] (v1) at (1,1) {y};
    \node[v] (v2) at (3,1) {z};
    \node[v] (v3) at (2,2) {k};
    \node[v] (v4) at (2,3.3) {x};

    \tedge{v1}{v3}{solid}{y}{above};
    \tedge{v2}{v3}{solid}{z}{above};
    \tedge{v3}{v4}{solid}{x}{right};

    % \draw (3.3,2.5) circle (1.9cm);
    % \draw (.7,2.5) circle (1.9cm);
    % \draw (2,.5) circle (1.9cm);
\end{tikzpicture}
\\
\begin{tikzpicture}
    \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
    \tikzstyle{e}=[]

    \node[v] (v1) at (0,  0) {kxyz};
    \node[v] (v2) at (-1,-1) {kxy};
    \node[v] (v3) at ( 1,-1) {kyz};
    \node[v] (v4) at (-2,-2) {kx};
    \node[v] (v5) at ( 0,-2) {ky};
    \node[v] (v6) at ( 2,-2) {kz};

    \tedge{v1}{v2}{solid}{}{};
    \tedge{v1}{v3}{solid}{}{};
    \tedge{v2}{v4}{solid}{}{};
    \tedge{v2}{v5}{solid}{}{};
    \tedge{v3}{v5}{solid}{}{};
    \tedge{v3}{v6}{solid}{}{};
\end{tikzpicture}
\begin{tikzpicture}
    \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
    \tikzstyle{e}=[]

    \node[v] (v1) at (0,  0) {kxyz};
    \node[v] (v2) at (-1,-1) {kxy};
    \node[v] (v3) at ( 1,-1) {kxz};
    \node[v] (v4) at (-2,-2) {kx};
    \node[v] (v5) at ( 0,-2) {ky};
    \node[v] (v6) at ( 2,-2) {kz};

    \tedge{v1}{v2}{solid}{}{};
    \tedge{v1}{v3}{solid}{}{};
    \tedge{v2}{v4}{solid}{}{};
    \tedge{v2}{v5}{solid}{}{};
    \tedge{v3}{v4}{solid}{}{};
    \tedge{v3}{v6}{solid}{}{};
\end{tikzpicture}
\begin{tikzpicture}
    \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
    \tikzstyle{e}=[]

    \node[v] (v1) at (0,  0) {kxyz};
    \node[v] (v2) at (-1,-1) {kxz};
    \node[v] (v3) at ( 1,-1) {kyz};
    \node[v] (v4) at (-2,-2) {kx};
    \node[v] (v5) at ( 0,-2) {ky};
    \node[v] (v6) at ( 2,-2) {kz};

    \tedge{v1}{v2}{solid}{}{};
    \tedge{v1}{v3}{solid}{}{};
    \tedge{v2}{v4}{solid}{}{};
    \tedge{v2}{v6}{solid}{}{};
    \tedge{v3}{v5}{solid}{}{};
    \tedge{v3}{v6}{solid}{}{};
\end{tikzpicture}
% \\
% \begin{tikzpicture}
%     \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
%     \tikzstyle{e}=[]

%     \node[v] (v1) at ( 0, 0) {kxyz};
%     \node[v] (v2) at (-1,-1) {kxy};
%     \node[v] (v3) at (-2,-2) {kx};
%     \node[v] (v4) at (-3,-3) {k};
%     \node[v] (v5) at ( 1,-1) {z plan};
%     \node[v] (v6) at ( 0,-2) {y plan};
%     \node[v] (v7) at (-1,-3) {x plan};
%     \node[v] (v8) at (-2,-4) {k plan};

%     \tedge{v1}{v2}{solid}{}{};
%     \tedge{v1}{v5}{solid}{}{};
%     \tedge{v2}{v3}{solid}{}{};
%     \tedge{v2}{v6}{solid}{}{};
%     \tedge{v3}{v4}{solid}{}{};
%     \tedge{v3}{v7}{solid}{}{};
%     \tedge{v4}{v8}{solid}{}{};
% \end{tikzpicture}

\caption{A well-constrained graph whose nodes are subgraphs labeled with their density. Below are its 3 optimal DR-Plans (partially complete). The center vertex has weight $k$ and is well-constrained itself. The radial nodes have weights $x,y,z \neq k$ with equivalent edge weights, making any union between $k$ and the others well-constrained. \todo{Make this figure more clear.}}
\label{3-plans}
\end{figure*}

In the case of a well-constrained graph, it is clear that there always exists a unique vertex-maximum DR-Plan that includes every single well-constrained vertex-maximal proper subgraph at each node, which we call the complete DR-plan. However, in the problem of the optimal DR-Plan there is no such unique plan. For instance, a graph that is formed by the union of 3 well-constrained subgraphs that all intersect on a well-constrained subgraph, demonstrated in Figure \ref{3-plans}. In this case, it results in $3$ unique optimal DR-Plans. Indeed, we will prove a union of $N$ well-constrained subgraphs will result in $N$ unique plans, but that at the $N^{\text{th}}$ level of the tree it will always be the same. Therefore, all choices of decomposition are in some sense equivalent. The theorem we seek to prove is thus:

@@

We develop this notion of the canonical optimal DR-plan by carefully considering the case of a union of any two nontrivial well-constrained vertex-maximal proper subgraphs of a well-constrained graph. By definition, any subgraph of a well-constrained graph will either be (1) trivial, (2) under-constrained, or (3) well-constrained. We will analyze all 3 possibilities in turn. These observations will lead to interesting properties that govern the behavior of optimal DR-plans on well-constrained graphs.

@@

\subsection{Relationships for the Union and Intersection of Well-Constrained Subgraphs}
For the following lemmas, we define $F_i$ and $F_j$ as well-constrained subgraphs of the same well-constrained graph $F$.
We wish to prove the following bijections:

@@

\subsection{Inferring Graph Structure from Union and Intersection Properties}

@@

    \item 2 cases: \todo{Uses 2D requirement:} $C_k=Idc(C,R'_i\cup R_j\cup D'_{i,j})$ and $C_k=Idc(C,R_i\cup R'_j\cup D'_{i,j})$ are not possible. The proof mirrors the previous case, except you must choose $C_i$ and $C_j$, respectively, here.

    \item 1 case: $C_k=Idc(C,R_i\cup R_j\cup D'_{i,j})$ is all that is left!
\end{itemize}

@@

\begin{proof}
If any intersection was not trivial, then it must be well-constrained. If $C_k\cap C_l$ were well-constrained, then by Lemma \ref{wc-l3} all of the intersections are well-constrained. This contradicts the statement that $C_i\cap C_j$ is trivial.
% It follows that if the intersection is trivial then the union is under-constrained (Lemma \ref{uc-l1}). If the union is under-constrained, then the
\end{proof}

@@

\subsection{Proving the Main Theorem}
Lemmas \ref{wc-l3} and \ref{uc-l2} show that $CompleteDRP(C)$ will result in one of two scenarios. (A) Either all $C_1,\ldots,C_N$ intersect on some common well-constrained subgraph and any two union to make $C$, or (B) all $C_1,\ldots,C_N$ intersect trivially and all of them must be unioned to make $C$.

@@

\begin{figure}\centering
\begin{tikzpicture}
    \draw[rotate=0]  (0,0) ellipse (1.5cm and .3cm);
    \draw[rotate around={-59:(.7,1.2)}] (.8,1.1) ellipse (1.5cm and .3cm);
    \draw[rotate around={59:(-.7,1.2)}] (-.8,1.1) ellipse (1.5cm and .3cm);

    % \draw[rotate around={59:(.7,-1.2)}] (.8,-1.1) ellipse (1.5cm and .3cm);
    % \draw[rotate around={-59:(-.7,-1.2)}] (-.8,-1.1) ellipse (1.5cm and .3cm);

    % \draw[rotate=0] (1,1) ellipse (.1cm and .1cm);
    % \draw[rotate=66] (0,0) ellipse (.1cm and .1cm);
\end{tikzpicture}
\begin{tikzpicture}
    \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
    \tikzstyle{el}=[draw, ellipse, minimum height=.75cm, minimum width=1.5cm]
    \tikzstyle{e}=[]

    \node[el] (m) at (0,    0) {k};
    \node[v]  (l) at (-1.5, 0) {b};
    \node[v]  (r) at (1.5,  0) {c};

    \node[el] (tl) at (-1,  1) {i};
    \node[el] (tr) at (1,   1) {j};
    \node[v]  (t)  at (0,   2) {a};

    % \node[el] (bl) at (-1,  -1) {l};
    % \node[el] (br) at (1,   -1) {m};
    % \node[v]  (b)  at (0,   -2) {d};

    % \node[el] (v2) at (-1,-1) {b};
    % \node[el] (v3) at (-1,-1) {b};
    % \node[el] (v4) at (-1,-1) {b};
    % \node[el] (v5) at (-1,-1) {b};

    \tedge{m}{l}{solid}{}{};
    \tedge{m}{r}{solid}{}{};

    \tedge{l}{tl}{solid}{}{};
    \tedge{tl}{t}{solid}{}{};
    \tedge{r}{tr}{solid}{}{};
    \tedge{tr}{t}{solid}{}{};

    % \tedge{l}{bl}{solid}{}{};
    % \tedge{bl}{b}{solid}{}{};
    % \tedge{r}{br}{solid}{}{};
    % \tedge{br}{b}{solid}{}{};
\end{tikzpicture}

\caption{Each node contains a subgraph of the entire, well-constrained graph $G$. We take $Idc(G,a\cup i\cup b)$, $Idc(G,a\cup j\cup c)$, and $Idc(G,b\cup k\cup c)$ to be well-constrained. If the union of any two of these listed unions is under-constrained then it immediately follows that all such unions are under-constrained and that nodes $a,b,c$ must all be trivial subgraphs.
% Each node contains a subgraph of the entire, well-constrained graph. We take $a\cup i\cup b$, $a\cup j\cup c$, $b\cup k\cup c$, $b\cup l\cup d$, and $c\cup m\cup d$ to be well-constrained. If the union of any two of these listed unions is under-constrained then it immediately follows that all such unions are under-constrained and that nodes $a,b,c,d$ must all be trivial subgraphs.
% THIS IS NOT TECHNICALLY CORRECT... $a\cup i\cup b$ doesn't include the edge between them... Is there a better way to phrase this?
}
\label{trivial-intersection}
\end{figure}

@@

In $OptimalDRP(G)$ of a well-constrained $G$, if $C_i \cap C_j$ is trivial (case (B)), then all $C_1,\ldots, C_N$ must be included in the optimal plan as children of $C$.
\end{theorem}

\begin{proof}
From Lemma \ref{uc-l1}, if it is trivial then $C_i \cup C_j$ must be under-constrained. If it is under-constrained, it must be part of some larger well-constrained subgraph $D$. If $D$ is not $G$ itself, then we just found a larger proper subgraph and the graphs in the set were not vertex-maximal to begin with.
 % For $C$ to be well-constrained... WHAT????

If there was some $X\subset [1,\ldots,N]$ such that $\bigcup_{i\in X}{C_i}\neq C$ but it was well-constrained, then we just found a larger proper subgraph and the graphs in the set were not vertex-maximal to begin with.

This means that in the case of a trivial intersection, all of the children come together to form some complex structure that is itself rigid. Such an example is shown in Figure \ref{trivial-intersection}.
\end{proof}

@@

In $OptimalDRP(G)$ of a well-constrained $G$, if $C_i \cup C_j$ is well-constrained (case (A)), then any 2 well-constrained vertex-maximal proper subgraphs of $C$ will be sufficient as its children.
% Namely, these children are any 2 of its well-constrained vertex-maximal proper subgraphs.
\end{theorem}

\begin{proof}
For a valid DR-plan, all children must be proper subgraphs. Therefore, for the union to be the parent (and satisfy the conditions of a DR-plan) there must be at least 2 children. It follows directly from Lemma \ref{wc-l2} that if there exists $C_i, C_j$ such that $C_i \cup C_j$ is well-constrained, then you found a tree with only 2 children.

Clearly, this is the optimal choice at this level. However, for it to be a solution to $OptimalDRP(G)$, it must not affect the maximum fan-in later on.

Take $\bigcap_{k=1}^N{C_k}$ to be the graph $D$. Take $R_k=C\setminus C_k$. This means that $D$ is also $\bigcup_{k=1}^N{R_k}$.

After we go down $N$ levels we get to a point where every node is some $Idc(C,R_k\cup D)$. Until this point, the fan-in of every node is exactly 2.

This is demonstrated with $N=3$ in Figure \ref{3-plans}. It is clear that until this point, the fan-in at every node is exactly 2 in the optimal solution. This follows from the discussion above. Now, at this level, the fan-in must be equal in all scenarios. In fact, at node $k$ it will be 1 (because of $D$ which is well-constrained) plus whatever fan-in $R_k$ incurs.
\end{proof}

With these two proofs, the original Theorem \ref{t1} has been proven. With this we have formulated the notion of a canonical optimal DR-plan. Any optimal DR-plan of a well-constrained graph must follow this pattern.

@@

\subsection{Further Results}

\begin{corollary}
Take $\bigcap_{k=1}^N{C_k}$ to be the graph $D$. If $D$ is well-constrained, then $D$ will be a descendant of every $C_k$.
\end{corollary}

\begin{proof}
Explained in Theorem \ref{wc-t1}.
\end{proof}

\begin{corollary}
$\forall i,j\in [1,\ldots,N]$ if $i\neq j$ there are no edges in $C$ between the vertices in subgraphs $C\setminus C_i$ and $C\setminus C_j$.
\end{corollary}

\begin{proof}
Further constraints between them would imply $C_i \cup C_j$ is a subgraph of $C$, but lemma \ref{wc-l2} proves is the entire graph.
\end{proof}

@@

\begin{corollary}
There is no rigid subgraph induced by a proper, nonempty subset of vertices of $V_i \setminus (V_1\cap V_2)$ and a subset of $V_1\cap V_2$ of size at least 2.
\end{corollary}

\begin{proof}
Since $C_1\cup C_2$ is the entire graph
\todo{Prove this!!!!}
\end{proof}

@@

>>>>

\section{The Canonical Decomposition-Recombination Plan}

\subsection{Theory}

% \begin{figure*}\centering
% \begin{tikzpicture}
%     \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
%     \tikzstyle{e}=[]

%     \node[v] (v1) at (1,1) {$R_j$};
%     \node[v] (v2) at (3,1) {$R_k$};
%     \node[v] (v3) at (2,2) {$D$};
%     \node[v] (v4) at (2,3.3) {$R_i$};

%     \tedge{v1}{v3}{solid}{}{above};
%     \tedge{v2}{v3}{solid}{}{above};
%     \tedge{v3}{v4}{solid}{}{right};
% \end{tikzpicture}
% \ldots with weights \ldots
% \begin{tikzpicture}
%     \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
%     \tikzstyle{e}=[]

%     \node[v] (v1) at (1,1) {y};
%     \node[v] (v2) at (3,1) {z};
%     \node[v] (v3) at (2,2) {k};
%     \node[v] (v4) at (2,3.3) {x};

%     \tedge{v1}{v3}{solid}{y}{above};
%     \tedge{v2}{v3}{solid}{z}{above};
%     \tedge{v3}{v4}{solid}{x}{right};

%     % \draw (3.3,2.5) circle (1.9cm);
%     % \draw (.7,2.5) circle (1.9cm);
%     % \draw (2,.5) circle (1.9cm);
% \end{tikzpicture}
% \\
% \begin{tikzpicture}
%     \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
%     \tikzstyle{e}=[]

%     \node[v] (v1) at (0,  0) {kxyz};
%     \node[v] (v2) at (-1,-1) {kxy};
%     \node[v] (v3) at ( 1,-1) {kyz};
%     \node[v] (v4) at (-2,-2) {kx};
%     \node[v] (v5) at ( 0,-2) {ky};
%     \node[v] (v6) at ( 2,-2) {kz};

%     \tedge{v1}{v2}{solid}{}{};
%     \tedge{v1}{v3}{solid}{}{};
%     \tedge{v2}{v4}{solid}{}{};
%     \tedge{v2}{v5}{solid}{}{};
%     \tedge{v3}{v5}{solid}{}{};
%     \tedge{v3}{v6}{solid}{}{};
% \end{tikzpicture}
% \begin{tikzpicture}
%     \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
%     \tikzstyle{e}=[]

%     \node[v] (v1) at (0,  0) {kxyz};
%     \node[v] (v2) at (-1,-1) {kxy};
%     \node[v] (v3) at ( 1,-1) {kxz};
%     \node[v] (v4) at (-2,-2) {kx};
%     \node[v] (v5) at ( 0,-2) {ky};
%     \node[v] (v6) at ( 2,-2) {kz};

%     \tedge{v1}{v2}{solid}{}{};
%     \tedge{v1}{v3}{solid}{}{};
%     \tedge{v2}{v4}{solid}{}{};
%     \tedge{v2}{v5}{solid}{}{};
%     \tedge{v3}{v4}{solid}{}{};
%     \tedge{v3}{v6}{solid}{}{};
% \end{tikzpicture}
% \begin{tikzpicture}
%     \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
%     \tikzstyle{e}=[]

%     \node[v] (v1) at (0,  0) {kxyz};
%     \node[v] (v2) at (-1,-1) {kxz};
%     \node[v] (v3) at ( 1,-1) {kyz};
%     \node[v] (v4) at (-2,-2) {kx};
%     \node[v] (v5) at ( 0,-2) {ky};
%     \node[v] (v6) at ( 2,-2) {kz};

%     \tedge{v1}{v2}{solid}{}{};
%     \tedge{v1}{v3}{solid}{}{};
%     \tedge{v2}{v4}{solid}{}{};
%     \tedge{v2}{v6}{solid}{}{};
%     \tedge{v3}{v5}{solid}{}{};
%     \tedge{v3}{v6}{solid}{}{};
% \end{tikzpicture}
% % \\
% % \begin{tikzpicture}
% %     \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
% %     \tikzstyle{e}=[]

% %     \node[v] (v1) at ( 0, 0) {kxyz};
% %     \node[v] (v2) at (-1,-1) {kxy};
% %     \node[v] (v3) at (-2,-2) {kx};
% %     \node[v] (v4) at (-3,-3) {k};
% %     \node[v] (v5) at ( 1,-1) {z plan};
% %     \node[v] (v6) at ( 0,-2) {y plan};
% %     \node[v] (v7) at (-1,-3) {x plan};
% %     \node[v] (v8) at (-2,-4) {k plan};

% %     \tedge{v1}{v2}{solid}{}{};
% %     \tedge{v1}{v5}{solid}{}{};
% %     \tedge{v2}{v3}{solid}{}{};
% %     \tedge{v2}{v6}{solid}{}{};
% %     \tedge{v3}{v4}{solid}{}{};
% %     \tedge{v3}{v7}{solid}{}{};
% %     \tedge{v4}{v8}{solid}{}{};
% % \end{tikzpicture}

% \caption{A well-constrained graph whose nodes are subgraphs labeled with their density. Below are its 3 optimal DR-Plans (partially complete). The center vertex has weight $k$ and is well-constrained itself. The radial nodes have weights $x,y,z \neq k$ with equivalent edge weights, making any union between $k$ and the others well-constrained. \todo{Make this figure more clear.}}
% \label{3-plans}
% \end{figure*}

In the problem of the optimal DR-Plan there is generally not a unique plan. For example, a graph that is formed by the union of 3 well-constrained subgraphs that all intersect on a well-constrained subgraph has ${3\choose 2} = 3$ unique optimal DR-Plans; any two of these subgraphs will suffice as children.
% Indeed, we will prove a union of $N$ well-constrained subgraphs will result in $N$ unique plans, but that at the $N^{\text{th}}$ level of the tree it will always be the same. Therefore, all choices of decomposition are in some sense equivalent. The theorem we seek to prove is thus:
However, we will show that regardless of which children are chosen for the plan, the recombination will require solving of the same systems. Thus, this definition of an optimal DR-plan could be considered the canonical DR-plan. To assist in showing this, we prove this core theorem throughout this section:

@@

% We develop this notion of the canonical optimal DR-plan by carefully considering the case of a union of any two nontrivial well-constrained vertex-maximal proper subgraphs of a well-constrained graph. By definition, any subgraph of a well-constrained graph will either be (1) trivial, (2) under-constrained, or (3) well-constrained. We will analyze all 3 possibilities in turn. These observations will lead to interesting properties that govern the behavior of optimal DR-plans on well-constrained graphs.

@@

\subsubsection{Relationships for the Union and Intersection of Well-Constrained Subgraphs}
For the following lemmas, we define $F_i$ and $F_j$ as well-constrained subgraphs of the same well-constrained graph $F$.
We wish to prove the following bijections:

@@

\subsubsection{Inferring Parent Structure from Union and Intersection of Children}

@@

    \item 2 cases: \todo{Uses 2D requirement:} $C_k=Idc(C,R'_i\cup R_j\cup D'_{i,j})$ and $C_k=Idc(C,R_i\cup R'_j\cup D'_{i,j})$ are not possible. The proof mirrors the previous case, except here you must choose $C_i$ and $C_j$ respectively.

    \item 1 case: $C_k=Idc(C,R_i\cup R_j\cup D'_{i,j})$ is all that remains.
\end{itemize}

@@

\begin{proof}
If some $C_i\cap C_k$ is not trivial, then it must be well-constrained. Then, by Lemma \ref{wc-l3}, all of the intersections are well-constrained. This contradicts the statement that $C_i\cap C_j$ is trivial.
% It follows that if the intersection is trivial then the union is under-constrained (Lemma \ref{uc-l1}). If the union is under-constrained, then the
\end{proof}

@@

\subsubsection{Proving the Main Theorem \ref{t1}}\label{sec:maintheorem}
Lemmas \ref{wc-l3} and \ref{uc-l2} show that $CompleteDRP(C)$ will result in one of two scenarios. (A) Either all $C_1,\ldots,C_N$ intersect on some common well-constrained subgraph and any two union to make $C$, or (B) all $C_1,\ldots,C_N$ intersect trivially and all of them must be unioned to make $C$.

@@

% \begin{figure}\centering
% \begin{tikzpicture}
%     \draw[rotate=0]  (0,0) ellipse (1.5cm and .3cm);
%     \draw[rotate around={-59:(.7,1.2)}] (.8,1.1) ellipse (1.5cm and .3cm);
%     \draw[rotate around={59:(-.7,1.2)}] (-.8,1.1) ellipse (1.5cm and .3cm);

%     % \draw[rotate around={59:(.7,-1.2)}] (.8,-1.1) ellipse (1.5cm and .3cm);
%     % \draw[rotate around={-59:(-.7,-1.2)}] (-.8,-1.1) ellipse (1.5cm and .3cm);

%     % \draw[rotate=0] (1,1) ellipse (.1cm and .1cm);
%     % \draw[rotate=66] (0,0) ellipse (.1cm and .1cm);
% \end{tikzpicture}
% \begin{tikzpicture}
%     \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
%     \tikzstyle{el}=[draw, ellipse, minimum height=.75cm, minimum width=1.5cm]
%     \tikzstyle{e}=[]

%     \node[el] (m) at (0,    0) {k};
%     \node[v]  (l) at (-1.5, 0) {b};
%     \node[v]  (r) at (1.5,  0) {c};

%     \node[el] (tl) at (-1,  1) {i};
%     \node[el] (tr) at (1,   1) {j};
%     \node[v]  (t)  at (0,   2) {a};

%     % \node[el] (bl) at (-1,  -1) {l};
%     % \node[el] (br) at (1,   -1) {m};
%     % \node[v]  (b)  at (0,   -2) {d};

%     % \node[el] (v2) at (-1,-1) {b};
%     % \node[el] (v3) at (-1,-1) {b};
%     % \node[el] (v4) at (-1,-1) {b};
%     % \node[el] (v5) at (-1,-1) {b};

%     \tedge{m}{l}{solid}{}{};
%     \tedge{m}{r}{solid}{}{};

%     \tedge{l}{tl}{solid}{}{};
%     \tedge{tl}{t}{solid}{}{};
%     \tedge{r}{tr}{solid}{}{};
%     \tedge{tr}{t}{solid}{}{};

%     % \tedge{l}{bl}{solid}{}{};
%     % \tedge{bl}{b}{solid}{}{};
%     % \tedge{r}{br}{solid}{}{};
%     % \tedge{br}{b}{solid}{}{};
% \end{tikzpicture}

% \caption{Each node contains a subgraph of the entire, well-constrained graph $G$. We take $Idc(G,a\cup i\cup b)$, $Idc(G,a\cup j\cup c)$, and $Idc(G,b\cup k\cup c)$ to be well-constrained. If the union of any two of these listed unions is under-constrained then it immediately follows that all such unions are under-constrained and that nodes $a,b,c$ must all be trivial subgraphs.
% % Each node contains a subgraph of the entire, well-constrained graph. We take $a\cup i\cup b$, $a\cup j\cup c$, $b\cup k\cup c$, $b\cup l\cup d$, and $c\cup m\cup d$ to be well-constrained. If the union of any two of these listed unions is under-constrained then it immediately follows that all such unions are under-constrained and that nodes $a,b,c,d$ must all be trivial subgraphs.
% % THIS IS NOT TECHNICALLY CORRECT... $a\cup i\cup b$ doesn't include the edge between them... Is there a better way to phrase this?
% }
% \label{trivial-intersection}
% \end{figure}

In $OptimalDRP(G)$ of a well-constrained $G$, if $C_i \cup C_j$ is well-constrained, then any 2 well-constrained vertex-maximal proper subgraphs of $C$ will be sufficient as its children.
% Namely, these children are any 2 of its well-constrained vertex-maximal proper subgraphs.
\end{theorem}

\begin{proof}
In a valid DR-plan, all children must be proper subgraphs. Therefore, for the union to be the parent (and satisfy the conditions of a DR-plan) there must be at least two children. It follows directly from Lemma \ref{wc-l3} that if there exists $C_i, C_j$ such that $C_i \cup C_j$ is well-constrained, then the smallest fan-in at this node can be made by selecting any two $C_i, C_j$.
% you found a tree with only 2 children.
% Clearly, this is the optimal choice at this level.
However, for it to be a solution to $OptimalDRP(G)$, it must not affect the maximum fan-in for any descendant.

Take $D=\bigcap_{k=1}^N{C_k}$ and $R_k=C\setminus C_k$.
% This means that $D$ is also $\bigcup_{k=1}^N{R_k}$.
Suppose we select $i$ and $j$, where $i\neq j$, as the children. Since
% \[C_i=Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i\}}{R_k}\right)\]
% the children of this node will be
% \[Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i,m\}}{R_k}\right)\]
% and
% \[Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i,n\}}{R_k}\right)\]
$C_i=Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i\}}{R_k}\right)$
the children of this node will be
$Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i,m\}}{R_k}\right)$
and
$Idc\left(C,D\cup\bigcup_{k\in N\setminus\{i,n\}}{R_k}\right)$
for arbitrary $m$ and $n$, where $m\neq n$. This continues for $N-1$ levels total, always with fan-in of two, at which point every descendant of $C$ is some $Idc(C,D\cup R_k)$.

% This is demonstrated with $N=3$ in Figure \ref{3-plans}. It is clear that until this point, the fan-in at every node is exactly 2 in the optimal solution. This follows from the discussion above. Now, at this level, the fan-in must be equal in all scenarios. In fact, at node $k$ it will be 1 (because of $D$ which is well-constrained) plus whatever fan-in $R_k$ incurs.
\end{proof}

@@

In $OptimalDRP(G)$ of a well-constrained $G$, if $C_i \cap C_j$ is trivial, then all $C_1,\ldots, C_N$ must be included in the optimal plan as children of $C$.
\end{theorem}

% \begin{proof}
% From Lemma \ref{uc-l1}, if it is trivial then $C_i \cup C_j$ must be under-constrained. If it is under-constrained, it must be part of some larger well-constrained subgraph $D$. If $D$ is not $C$ itself, then we just found a larger proper subgraph and the graphs in the set were not vertex-maximal to begin with.
%  % For $C$ to be well-constrained... WHAT????

% If there was some $X\subset [1,\ldots,N]$ such that $\bigcup_{i\in X}{C_i}\neq C$ but it was well-constrained, then we just found a larger proper subgraph and the graphs in the set were not vertex-maximal to begin with.

% This means that in the case of a trivial intersection, all of the children come together to form some complex structure that is itself rigid. Such an example is shown in Figure \ref{trivial-intersection}.
% \end{proof}

\begin{proof}
Take $X\subset \{1,\ldots,N\}$ and $D=\bigcup_{i\in X}{C_i}$. If $D\neq C$ but it was well-constrained, then we just found a larger proper subgraph and the graphs in the set were not vertex-maximal to begin with.

\todo{Uses 2D requirement:}
If $D= C$, then we contradict the assumption that $C_i \cap C_j$ is trivial. By Lemma \ref{uc-l2}, if $C_i \cap C_j$ is trivial then for $k\notin X$, $D\cap C_k$ must be one or more trivial subgraphs. Furthermore, by definition of a DR-plan, $C_k=C\cap C_k=D\cap C_k$. Together, this shows that $C_k$ cannot be well-constrained, violating the properties of a DR-plan.
\end{proof}

@@

With these two proofs, the original Theorem \ref{t1} has been proven. With this we have formulated the notion of a canonical DR-plan.
% Any optimal DR-plan of a well-constrained graph must follow this pattern.
No matter which two children you choose in case (A) the recombination steps will always involve the same systems; in case (B), all children must always be included.

@@

% \subsection{Further Results}

% \begin{corollary}
% Take $\bigcap_{k=1}^N{C_k}$ to be the graph $D$. If $D$ is well-constrained, then $D$ will be a descendant of every $C_k$.
% \end{corollary}

% \begin{proof}
% Explained in Theorem \ref{wc-t1}.
% \end{proof}

% \begin{corollary}
% $\forall i,j\in [1,\ldots,N]$ if $i\neq j$ there are no edges in $C$ between the vertices in subgraphs $C\setminus C_i$ and $C\setminus C_j$.
% \end{corollary}

% \begin{proof}
% Further constraints between them would imply $C_i \cup C_j$ is a subgraph of $C$, but lemma \ref{wc-l2} proves is the entire graph.
% \end{proof}

@@

% \begin{corollary}
% There is no rigid subgraph induced by a proper, nonempty subset of vertices of $V_i \setminus (V_1\cap V_2)$ and a subset of $V_1\cap V_2$ of size at least 2.
% \end{corollary}

% \begin{proof}
% Since $C_1\cup C_2$ is the entire graph
% \todo{Prove this!!!!}
% \end{proof}

@@

\subsection{Examples}

We now present two examples of non-tree-decomposable graphs that illustrate the two cases found in decomposition -- intersection on a well-constrained subgraph and intersection on a trivial subgraph.

\begin{figure*}\centering
\begin{tikzpicture}[scale=3]
    \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
    \tikzstyle{e}=[]

    \node[v] (v1) at (0,0.866) {$a_1$};
    \node[v] (v2) at (-1,-0.866) {$a_2$};
    \node[v] (v3) at (1,-0.866) {$a_3$};

    \node[v] (v4) at (0,0.577-.1) {$b_1$};
    \node[v] (v5) at (-0.667,-0.577-.1) {$b_2$};
    \node[v] (v6) at (0.667,-0.577-.1) {$b_3$};

    \node[v] (v7) at (0,0.289-.2) {$c_1$};
    \node[v] (v8) at (-0.333,-0.289-.2) {$c_2$};
    \node[v] (v9) at (0.333,-0.289-.2) {$c_3$};

    \tedge{v1}{v2}{solid}{}{};
    \tedge{v1}{v3}{solid}{}{};
    \tedge{v2}{v3}{solid}{}{};

    \tedge{v4}{v5}{solid}{}{};
    \tedge{v4}{v6}{solid}{}{};
    \tedge{v5}{v6}{solid}{}{};

    \tedge{v7}{v8}{solid}{}{};
    \tedge{v7}{v9}{solid}{}{};
    \tedge{v8}{v9}{solid}{}{};

    \tedge{v1}{v4}{solid}{}{};
    \tedge{v2}{v5}{solid}{}{};
    \tedge{v3}{v6}{solid}{}{};

    \tedge{v4}{v7}{solid}{}{};
    \tedge{v5}{v8}{solid}{}{};
    \tedge{v6}{v9}{solid}{}{};
\end{tikzpicture}

\begin{tikzpicture}
    \tikzstyle{v}=[draw, circle, minimum size=0.75cm]
    \tikzstyle{e}=[]

    \node (c0) at (0,0) {$\{a_1,a_2,a_3,b_1,b_2,b_3,c_1,c_2,c_3\}$};
    \node (c1a) at (-2,-1) {$\{a_1,a_2,a_3,b_1,b_2,b_3\}$};
    \node (c1b) at (2,-1) {$\{b_1,b_2,b_3,c_1,c_2,c_3\}$};
    \node (c2a) at (-2,-2) {$\{a_1,a_2,a_3\}$};
    \node (c2b) at (0,-2) {$\{b_1,b_2,b_3\}$};
    \node (c2c) at (2,-2) {$\{c_1,c_2,c_3\}$};
    \node (c2ab1) at (-5.6,-2) {$\{a_1,b_1\}$};
    \node (c2ab2) at (-4.5,-2) {$\{a_2,b_2\}$};
    \node (c2ab3) at (-3.4,-2) {$\{a_3,b_3\}$};
    \node (c2bc1) at (5.6,-2) {$\{b_1,c_1\}$};
    \node (c2bc2) at (4.5,-2) {$\{b_2,c_2\}$};
    \node (c2bc3) at (3.4,-2) {$\{b_3,c_3\}$};

    \tedge{c0}{c1a}{solid}{}{};
    \tedge{c0}{c1b}{solid}{}{};

    \tedge{c1a}{c2ab1}{solid}{}{};
    \tedge{c1a}{c2ab2}{solid}{}{};
    \tedge{c1a}{c2ab3}{solid}{}{};
    \tedge{c1a}{c2a}{solid}{}{};
    \tedge{c1a}{c2b}{solid}{}{};

    \tedge{c1b}{c2bc1}{solid}{}{};
    \tedge{c1b}{c2bc2}{solid}{}{};
    \tedge{c1b}{c2bc3}{solid}{}{};
    \tedge{c1b}{c2b}{solid}{}{};
    \tedge{c1b}{c2c}{solid}{}{};
\end{tikzpicture}
